Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-02 paper/paper.tex
Update paper

The tool is implemented in Python in about 2K lines of code according to the LOC
metric, and has only two Python dependencies so far, at the cost of the
dependency on the operating system interfaces for which we choose POSIX as a
widespread openly available standard. Needless to say, we used Litrepl to
evaluate and verify the examples presented in this document.

>>>>

The tool is implemented in Python in under 2K lines of code according to the LOC
metric, and has only two Python dependencies so far, at the cost of the
dependency on the POSIX operating system interfaces. Needless to say, we used
Litrepl to evaluate and verify the examples presented in this document.
